---
title: "Data Take Two"
output: 
  html_notebook: 
    toc: yes
    toc_float: yes
---

#Question 1: Roaming outdoor cats harm wildlife
A high number strongly agrees whereas a low number disagrees. 

####Question 1A: Roaming outdoor cats harm wildlife.

Answers:  Strongly Agree = 7
            Moderately Agree = 6
            Slightly Agree = 5
            Neither Agree or Disagree = 4
            Slightly Disagree = 3
            Moderately Disagree = 2
            Strongly Disagree = 1
          
####Question 1B: Roaming outdoor cats do not harm wildlife.

Answers:  Strongly Agree = 1
            Moderately Agree = 2
            Slightly Agree = 3
            Neither Agree or Disagree = 4
            Slightly Disagree = 5
            Moderately Disagree = 6
            Strongly Disagree = 7
            
```{r}

library(car)

df <- read.csv(file = "Raw_Data2.csv")

df$A1Num <- as.numeric(df$A1)

Q1A <- df[df[, "Q1"]=="Roaming outdoor cats harm wildlife",]
Q1A <- Q1A[, c(1,2,3,12:17)]
Q1A$A1Num <- recode(Q1A$A1Num,"1=6;2=2;3=4;4=5;5=3;6=7;7=1")

Q1B <- df[df[, "Q1"]=="Roaming outdoor cats do not harm wildlife",]
Q1B <- Q1B[, c(1,2,3,12:17)]
Q1B$A1Num <- recode(Q1B$A1Num,"1=2;2=6;3=4;4=3;5=5;6=1;7=7")


A <- as.numeric(Q1A$A1Num)
B <- as.numeric(Q1B$A1Num)



barplot(table(A), main = "Roaming outdoor cats HARM wildlife",xlab = "Disagree -> Neutral -> Agree",col = "light blue")
barplot(table(B),main = "Roaming Cats DO NOT harm Wildlife",xlab = "Agree -> Neutral -> Disagree", col = "light blue")


Data <- data.frame(
       WtAnswer=c(A, B),
       Question =factor(rep(c("A", "B"), times=c(length(A), length(B))))
       )


m <- aov(WtAnswer~Question,data = Data)
summary(m)

shapiro.test(Data$WtAnswer)

print("From the output, the p-value < 0.05 implying that the distribution of the data are  significantly different from normal distribution. In other words, we can NOT assume the normality.")

kruskal.test(WtAnswer ~ Question, data = Data) 

print("At .05 significance level, we conclude that the two questions have different answers.")

fligner.test(WtAnswer ~ Question, data = Data)




```

#Question 2: People should keep their cats indoors
A high number strongly agrees whereas a low number disagrees. 

###Question 2A: People should keep their cats indoors or under a person's control (e.g., leash, catio) while outdoorse.

Answers:  Strongly Agree = 7
            Moderately Agree = 6
            Slightly Agree = 5
            Neither Agree or Disagree = 4
            Slightly Disagree = 3
            Moderately Disagree = 2
            Strongly Disagree = 1
          
###Question 2B: People need not keep their cats indoors or under a person's control (e.g., leash, catio) while outdoors.

Answers:  Strongly Agree = 1
            Moderately Agree = 2
            Slightly Agree = 3
            Neither Agree or Disagree = 4
            Slightly Disagree = 5
            Moderately Disagree = 6
            Strongly Disagree = 7
```{r}
df <- read.csv(file = "Raw_Data2.csv")

df$A2Num <- as.numeric(df$A2)

Q2A <- df[df[, "Q2"]=="People should keep their cats indoors or under a person's control (e.g., leash, catio) while outdoors",]

Q2A <- Q2A[, c(1,4,5,12:17)]
Q2A$A2Num <- recode(Q2A$A2Num,"1=6;2=2;3=4;4=5;5=3;6=7;7=1")

Q2B <- df[df[, "Q2"]=="People need not keep their cats indoors or under a person's control (e.g., leash, catio) while outdoors",]
Q2B <- Q2B[, c(1,4,5,12:17)]
Q2B$A2Num <- recode(Q2B$A2Num,"1=2;2=6;3=4;4=3;5=5;6=1;7=7")


A <- as.numeric(Q2A$A2Num)
B <- as.numeric(Q2B$A2Num)


barplot(table(A), main = "People SHOULD keep their cats indoors",xlab = "Disagree -> Neutral -> Agree",col = "light blue")
barplot(table(B),main = "People need NOT keep their cats indoors",xlab = "Agree -> Neutral -> Disagree", col = "light blue")


Data <- data.frame(
       WtAnswer=c(A, B),
       Question =factor(rep(c("A", "B"), times=c(length(A), length(B))))
       )


m <- aov(WtAnswer~Question,data = Data)
summary(m)

shapiro.test(Data$WtAnswer)

print("From the output, the p-value < 0.05 implying that the distribution of the data are  significantly different from normal distribution. In other words, we can NOT assume the normality.")

kruskal.test(WtAnswer ~ Question, data = Data) 

print("At .05 significance level, we conclude that the two questions have different answers.")
```

#Question 3: Pet cats should be spayed or neutered
A high number strongly agrees whereas a low number disagrees. 

###Question 3A: Pet cats should be spayed or neutered unless intended for breeding.

Answers:  Strongly Agree = 7
            Moderately Agree = 6
            Slightly Agree = 5
            Neither Agree or Disagree = 4
            Slightly Disagree = 3
            Moderately Disagree = 2
            Strongly Disagree = 1
          
###Question 3B: Pet cats not intended for breeding need not be spayed or neutered.

Answers:  Strongly Agree = 1
            Moderately Agree = 2
            Slightly Agree = 3
            Neither Agree or Disagree = 4
            Slightly Disagree = 5
            Moderately Disagree = 6
            Strongly Disagree = 7
```{r}
df <- read.csv(file = "Raw_Data2.csv")

df$A3Num <- as.numeric(df$A3)

Q3A <- df[df[, "Q3"]=="Pet cats should be spayed or neutered unless intended for breeding",]
Q3A <- Q3A[, c(1,6,7,12:17)]
Q3A$A3Num <- recode(Q3A$A3Num,"1=6;2=2;3=4;4=5;5=3;6=7;7=1")

Q3B <- df[df[, "Q3"]=="Pet cats not intended for breeding need not be spayed or neutered",]
Q3B <- Q3B[, c(1,6,7,12:17)]
Q3B$A3Num <- recode(Q3B$A3Num,"1=2;2=6;3=4;4=3;5=5;6=1;7=7")


A <- as.numeric(Q3A$A3Num)
B <- as.numeric(Q3B$A3Num)


barplot(table(A), main = "Pet cats should be spayed or neutered", xlab = "Disagree -> Neutral -> Agree",col = "light blue")
barplot(table(B),main = "Pet cats need not be spayed or neutered",xlab = "Agree -> Neutral -> Disagree", col = "light blue")


Data <- data.frame(
       WtAnswer=c(A, B),
       Question =factor(rep(c("A", "B"), times=c(length(A), length(B))))
       )


m <- aov(WtAnswer~Question,data = Data)
summary(m)

shapiro.test(Data$WtAnswer)

print("From the output, the p-value < 0.05 implying that the distribution of the data are  significantly different from normal distribution. In other words, we can NOT assume the normality.")

kruskal.test(WtAnswer ~ Question, data = Data) 

print("At .05 significance level, we conclude that the two questions have different answers.")
```
#Question 4: Pet cats should be microchipped
A high number strongly agrees whereas a low number disagrees. 

###Question 4A: Pet cats should be microchipped (a microchip is a small identification device inserted under the animal's skin).

Answers:  Strongly Agree = 7
            Moderately Agree = 6
            Slightly Agree = 5
            Neither Agree or Disagree = 4
            Slightly Disagree = 3
            Moderately Disagree = 2
            Strongly Disagree = 1
          
###Question 4B: Pet cats need not be microchipped (a microchip is a small identification device inserted under the animal's skin).

Answers:  Strongly Agree = 1
            Moderately Agree = 2
            Slightly Agree = 3
            Neither Agree or Disagree = 4
            Slightly Disagree = 5
            Moderately Disagree = 6
            Strongly Disagree = 7
```{r}
df <- read.csv(file = "Raw_Data2.csv")

df$A4Num <- as.numeric(df$A4)

Q4A <- df[df[,"Q4"]=="Pet cats should be microchipped (a microchip is a small identification device inserted under the animal's skin)<br>",]
Q4A <- Q4A[, c(1,8,9,12:17)]
Q4A$A4Num <- recode(Q4A$A4Num,"1=6;2=2;3=4;4=5;5=3;6=7;7=1")

Q4B <- df[df[, "Q4"]=="Pet cats need not be microchipped (a microchip is a small identification device inserted under the animal's skin)",]
Q4B <- Q4B[, c(1,8,9,12:17)]
Q4B$A4Num <- recode(Q4B$A4Num,"1=2;2=6;3=4;4=3;5=5;6=1;7=7")


A <- as.numeric(Q4A$A4Num)
B <- as.numeric(Q4B$A4Num)



barplot(table(A), main = "Pet cats should be microchipped", xlab = "Disagree -> Neutral -> Agree",col = "light blue")
barplot(table(B),main = "Pet cats need not be microchipped",xlab = "Agree -> Neutral -> Disagree", col = "light blue")


Data <- data.frame(
       WtAnswer=c(A, B),
       Question =factor(rep(c("A", "B"), times=c(length(A), length(B))))
       )


m <- aov(WtAnswer~Question,data = Data)
summary(m)

shapiro.test(Data$WtAnswer)

print("From the output, the p-value < 0.05 implying that the distribution of the data are  significantly different from normal distribution. In other words, we can NOT assume the normality.")

kruskal.test(WtAnswer ~ Question, data = Data) 

print("At .05 significance level, we conclude that the two questions have different answers.")
```

#Question 5: Roaming outdoor cats pose a risk to human health
A high number strongly agrees whereas a low number disagrees. 

###Question 5A: Roaming outdoor cats pose a risk to human health.

Answers:  Strongly Agree = 7
            Moderately Agree = 6
            Slightly Agree = 5
            Neither Agree or Disagree = 4
            Slightly Disagree = 3
            Moderately Disagree = 2
            Strongly Disagree = 1
          
###Question 5B: Roaming outdoor cats do not pose a risk to human health.

Answers:  Strongly Agree = 1
            Moderately Agree = 2
            Slightly Agree = 3
            Neither Agree or Disagree = 4
            Slightly Disagree = 5
            Moderately Disagree = 6
            Strongly Disagree = 7
```{r}
df <- read.csv(file = "Raw_Data2.csv")

df$A5Num <- as.numeric(df$A5)

Q5A <- df[df[,"Q5"]=="Roaming outdoor cats pose a risk to human health<br>",]
Q5A <- Q5A[, c(1,10,11,12:17)]
Q5A$A5Num <- recode(Q5A$A5Num,"1=6;2=2;3=4;4=5;5=3;6=7;7=1")

Q5B <- df[df[, "Q5"]=="Roaming outdoor cats do not pose a risk to human health",]
Q5B <- Q5B[, c(1,10,11,12:17)]
Q5B$A5Num <- recode(Q5B$A5Num,"1=2;2=6;3=4;4=3;5=5;6=1;7=7")


A <- as.numeric(Q5A$A5Num)
B <- as.numeric(Q5B$A5Num)


barplot(table(A), main = "Roaming outdoor cats pose a risk to human health", xlab = "Disagree -> Neutral -> Agree",col = "light blue")
barplot(table(B),main = "Roaming outdoor cats do not pose a risk to human health",xlab = "Agree -> Neutral -> Disagree", col = "light blue")


Data <- data.frame(
       WtAnswer=c(A, B),
       Question =factor(rep(c("A", "B"), times=c(length(A), length(B))))
       )


m <- aov(WtAnswer~Question,data = Data)
summary(m)

shapiro.test(Data$WtAnswer)

print("From the output, the p-value < 0.05 implying that the distribution of the data are  significantly different from normal distribution. In other words, we can NOT assume the normality.")

kruskal.test(WtAnswer ~ Question, data = Data) 

print("At .05 significance level, we conclude that the two questions have different answers.")
```